### 2016-05-05 templates/report/dissemination/tex/disseminations.tex

{% autoescape off %}
{% block content %}

{% if type == 'i' %}
    \begin{longtable}{ |p{4cm}|p{4cm}|p{5cm}|p{2cm}| }
    Title & Topics & URL & Date \\
    \hline
    {% for dissemination in disseminations %}
        {{ dissemination.title }} & {{ dissemination.topics }} & {{ dissemination.link }} & {{ dissemination.date|date:"M d, Y" }} \\
    \hline
    {% endfor %}
    \end{longtable}

{% elif type == 'e' %}
    \begin{longtable}{ |p{3cm}|p{2,3cm}|p{2cm}|p{3cm}|p{3,5cm}|p{1,2cm}| }
    \hline
    \textbf{Title} & \textbf{Authors} & Media outlet & Topics & URL & Date \\
    \hline
    {% for dissemination in disseminations %}
        {{ dissemination.title }} & {{ dissemination.external.authors }} & {{ dissemination.external.media_outlet }} & {{ dissemination.topics }} & {{ dissemination.link }}&#125; & {{ dissemination.date|date:"M d, Y" }} \\
    \hline
    {% endfor %}
    \end{longtable}
{% endif %}

{% endblock %}
{% endautoescape %}

>>>>

{% autoescape off %}{% block content %}{% if type == 'i' %}\begin{longtable}{ |p{4cm}|p{4cm}|p{5cm}|p{2cm}| }
\hline
Title & Topics & URL & Date \\ \hline
{% for dissemination in disseminations %}{{ dissemination.title }} & {{ dissemination.topics }} & {{ dissemination.link }} & {{ dissemination.date|date:"M d, Y" }} \\ \hline {% endfor %}
\end{longtable}
{% elif type == 'e' %}
\begin{longtable}{ |p{3cm}|p{2,3cm}|p{2cm}|p{3cm}|p{3,5cm}|p{1,2cm}| }
\hline
Title & Authors & Media outlet & Topics & URL & Date \\ \hline
{% for dissemination in disseminations %}{{ dissemination.title }} & {{ dissemination.external.authors }} & {{ dissemination.external.media_outlet }} & {{ dissemination.topics }} & {{ dissemination.link }} & {{ dissemination.date|date:"M d, Y" }} \\ \hline {% endfor %}
\end{longtable}
{% endif %}
{% endblock %}
{% endautoescape %}
